### 2022-06-27 manuscript/manuscript.Rmd
sentence correction
sentence reword

These magnitude increases in data volume require the development of computationally efficient processing routines, especially for processing large sample sets.
Spectral artefacts such as Gibbs oscillations that are common in Fourier Transform based MS adds further complexity [@marshall2008].
Similarly, the alignment of spectra between samples can also make processing difficult over long analytical runs containing many samples [@draper2013].
Approaches such as the *proFIA* R package have already attempted to overcome some of these challenges [@delabriere2017].

@@

Mass spectra were acquired on an Exactive Orbitrap (ThermoFinnigan, San Jose CA) mass spectrometer, which was coupled to an Accela (ThermoFinnigan, San Jose CA) ultra-performance liquid chromatography system. 
A sample volume of 20 $\mu$L was injected and delivered to the electro-spray ionisation (ESI) source via a 'plug' flow solvent of pre-mixed HPLC grade MeOH (Fisher Scientific) and ultra-pure H~2~O (18.2 $\Omega$) at a ratio of 7:3. 
The initial flow rate was 60 $\mu$L min^-1^ for 0.4 minutes and increased to 200 $\mu$L min^-1^ over 0.8 minutes. 
The flow rate was maintained at 200 $\mu$L min^-1^ for 0.3 minutes then increased to 600 $\mu$L min^-1^ over 1.5 minutes. 
Then the flow rate was then returned to 60 $\mu$L min^-1^ for 0.5 minutes. 
The total gradient time was 3.5 minutes. The capillary temperature and voltage were set at 270 ^$\circ$^C and 37.50 kV respectively.

>>>>

These magnitude increases in data volume require the development of computationally efficient processing routines, especially for processing large sample sets.
Spectral artefacts such as Gibbs oscillations, that are common in Fourier Transform based MS, adds further complexity [@marshall2008].
Similarly, the alignment of mass spectra between samples can also make processing difficult, especially in analytical runs containing many samples [@draper2013].
Approaches such as the *proFIA* R package have already attempted to overcome some of these challenges [@delabriere2017].

@@

Mass spectra were acquired on an Exactive Orbitrap (ThermoFinnigan, San Jose CA) mass spectrometer, which was coupled to an Accela (ThermoFinnigan, San Jose CA) ultra-performance liquid chromatography system. 
A sample volume of 20 $\mu$L was injected and delivered to the electro-spray ionisation (ESI) source via a 'plug' flow solvent of pre-mixed HPLC grade MeOH (Fisher Scientific) and ultra-pure H~2~O (18.2 $\Omega$) at a ratio of 7:3. 
The initial flow rate was 60 $\mu$L min^-1^ for 0.4 minutes and increased to 200 $\mu$L min^-1^ over 0.8 minutes. 
The flow rate was maintained at 200 $\mu$L min^-1^ for 0.3 minutes then increased to 600 $\mu$L min^-1^ over 1.5 minutes. 
Then the flow rate was returned to 60 $\mu$L min^-1^ for 0.5 minutes. 
The total gradient time was 3.5 minutes. The capillary temperature and voltage were set at 270 ^$\circ$^C and 37.50 kV respectively.
